Implicit yaddayadda

### 2011-10-24 papers/PLDI2012/implicitization.tex

>>>>

In order to compare the various techniques, we compare by inclusion the obtained
abstract values at each control points in $P_R$.

In this section, our experimental results come from the analysis of various
open-source projects listed in Figure \ref{fig:projects}, written in C, C++ and
Fortran.
\begin{figure}[!h]
	\centering
\begin{tabular}{|l|l|l|} \hline
	Name & LOC & $|P_R|$ \\ \hline
	a2ps & 55k & 2012\\
	gawk & 59k & 902\\ 
	gnuchess & 38k & 1222\\ 
	gnugo & 83k & 2801\\
	grep & 35k & 820\\
	gzip & 27k & 494\\
	lapack/blas & 954k & 16422\\
	make & 34k & 993\\ 
	sed & 23k & 292\\
	tar & 73k & 1712\\
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{figure}

\subsection{Precision of the various techniques}

\begin{figure}[h]
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).}
  \label{fig:techniques}
\end {figure}

\JH{La comparaison DIS/G+PF n'est pas encore correcte (DIS pas compl\`etement
impl\'ement\'e)\\} 
Figures \ref{fig:techniques} shows the results of various comparisons between
the different analysis techniques.

\subsection{Precision of Abstract Domains}
